---
title: "Assignment 8"
author: "gzahn"
date: "March 23, 2019"
output:
  html_document:
    df_print: paged
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# **Assignment 8**

In this assignment, you will use R (within R-Studio) to:
  
+ Load and clean a real data set
+ Conduct exploratory analyses, including informative figures
+ Build and test appropriate models
+ Draw conclusions about your data
+ Combine all of the above into a well-documented R-Markdown report and export (knit) it into an HTML file

**All file paths should be relative, starting from the Assignment_8 directory!! (where you found this file)**

**This means that you need to create a new R-Project named "Assignment_8.Rproj" in your Assignment_8 directory, and work from scripts within that.**


## **For credit...**

1.  Push a completed version of your Rproj and R-markdown file (details at end of this assignment) to GitHub
2.  Your score will also depend on your analyses and presentation of your final report

____________

# Your tasks:

+ Use the data set "../../Data/GradSchool_Admissions.csv"
```{r}
df=read.csv("./GradSchool_Admissions.csv")
library(tidyverse)
library(MASS)
library(modelr)
```
+ You will explore and model the predictors of graduate school admission
  - the "admit" column is coded as 1=success and 0=failure
  - the other columns are the GRE score, the GPA, and the rank of the undergraduate institution, where I is "top-tier."
+ Document your data explorations, figures, and conclusions in a reproducible R-markdown report
```{r}
ggplot(df, aes(x=gpa,y=rank,col=admit)) + geom_jitter() + geom_smooth(method="lm")
ggplot(df, aes(x=gre,y=rank,col=admit)) + geom_jitter() + geom_smooth(method="lm")
ggplot(df, aes(x=gpa,y=admit,col=rank)) + geom_jitter() + geom_smooth(method="lm")
ggplot(df, aes(x=gre,y=admit,col=rank)) + geom_jitter() + geom_smooth(method="lm")
```

```{r}
mod1 = lm(admit ~ gre + gpa + rank, data = df)
summary(mod1)

mod2 = lm(admit ~ gre + gpa, data = df)
summary(mod2)


mod3 = lm(admit ~ gpa + rank, data = df)
summary(mod3)

```


```{r}
df = add_predictions(df, mod1, var= "mod1")
df = add_predictions(df, mod2, var= "mod2")
df = add_predictions(df, mod3, var="mod3")



df=mutate(df, DIFF1 = abs(mod1 -admit))
df=mutate(df, DIFF2 = abs(mod2 -admit))
df=mutate(df, DIFF3 = abs(mod3 -admit))

```

Predit which one is the best to use
```{r}
mean(df$DIFF1)
mean(df$DIFF2)
mean(df$DIFF3)

anova(mod1, mod2)
anova(mod2, mod3)
anova(mod1,mod3)

stepAIC(mod1)
stepAIC(mod2)
stepAIC(mod3)
```

```{r}
df = add_predictions(df, mod1, var= "mod1")
df = add_predictions(df, mod2, var= "mod2")
df = add_predictions(df, mod3, var="mod3")

```

Graph of the different predictive models
Mod1 = Red
Mod2 = Blue
Mod3 = Green

```{r}
ggplot(df, aes(x=gre)) +
  geom_jitter(aes(y=admit), alpha=.5) +
  geom_jitter(aes(y=mod1), color="Red") +
  geom_jitter(aes(y=mod2), color="Blue") + 
  geom_jitter(aes(y=mod3), color="Green") 

```



Just for fun does GPA predit GRE Scores?

```{r}

mod4 =lm(gre ~ gpa, data= df)
summary(mod4)
ggplot(df, aes(x=gpa,y=gre,col=admit)) +geom_point() + geom_smooth(method="lm")

```


